\section{Introduction}\label{sec:introduction}

The goal of this project is to design and implement RouteChasm, a full-stack web framework focused on ease of development,
extensibility, and AI generation tooling.
RouteChasm aims to define an abstraction layer for content rendering, routing, database access, multilingual support,
form handling, and component-based web-page editor with AI generated components.
The intention is to make full-stack development faster and more straightforward by unifying all layers of abstraction.
Achieving this requires implementing all features by hand and avoiding reliance on third-party libraries.

\subsection{Tasks}\label{subsec:introduction-tasks}
To satisfy the goal, the project is divided into tasks :

\begin{itemize}
    \item Design extensible full-stack framework architecture.
    \item Implement the core framework components, including content rendering, routing, database model abstraction,
        multilingual support, and forms.
    \item Develop an editor subsystem capable of creating, manipulating, and deleting components.
    \item Implement AI generation of static webpage templates.
    \item Implement AI generation of components for the editor.
    \item Implement AI translation tooling for multilingual support.
\end{itemize}

\subsection{Hypothesis}\label{subsec:introduction-hypothesis}
Unified and convention-driven abstraction layer can streamline full-stack development.
AI generated content can drastically decrease time in content creation, but the system is brittle and still has learning curve.