\section{Requirements}\label{sec:requirements}
This section defines the functional and non-functional requirements of RouteChasm.

\subsection{Functional Requirements}\label{subsec:requirements-functional_requirements}

\subsubsection{Framework requirements}
\begin{itemize}
    \item The framework must provide a predictable routing system capable of mapping HTTP requests to handlers.
    \item Routing system must support HTTP methods.
    \item Routing system must be modular, such that part of the tree can be moved somewhere else and all the bindings
        work as expected.
    \item The framework has the ability to automatically generate CRUD operations for database tables.
    \item Models must map database columns in human-friendly way without boilerplate.
    \item CRUD endpoints must integrate with the form-handling subsystem.
    \item The system has the ability to automatically generate forms based on model structure.
    \item Developers must be able to override field labels, types, and validation rules.
    \item The framework must provide a component-based editor capable of assembling webpages from reusable components.
    \item Components must be entirely rendered on client from stored metadata describing their structure, fields, and configuration.
    \item The editor must support editing of component metadata.
\end{itemize}

\subsubsection{AI generation}
\begin{itemize}
    \item The system must include an AI-powered translation unit capable of translating text for supported languages.
    \item The system must be capable of translating dynamic text with variable.
    \item The framework must support generating new webpage components using AI\@.
    \item Users must be able to request static webpage templates that are created by the AI system.
    \item The AI generation process must follow the project’s naming conventions and structural constraints.
\end{itemize}

\subsection{Non-Functional Requirements}\label{subsec:requirements-non_functional_requirements}

\begin{itemize}
    \item The system must prioritize ease of development and readability.
    \item New modules, components, and templates must be easy to add and maintain.
    \item The framework must perform efficiently enough for small-to-medium projects.
    \item All core features must be implemented without relying on third-party PHP libraries to ensure full control and consistent behavior.
    \item Code must follow the conventions defined by the framework’s philosophy.
    \item Routing, models, forms, and components must follow a unified design approach.
    \item The editor, rendering system, and AI component generation must operate on the same metadata structures.
    \item CRUD operations, routing, and form generation must behave deterministically.
\end{itemize}
