\section{Technical research}\label{sec:techical-research}
This section provides context on some of the terms this project uses.

\subsection{CMS}\label{subsec:cms}
Content Management System is type of software that provides simple interface to create, manage, and publish digital
content without programming language.
Most of the time the system controls blogging websites or e-shops.

\subsection{AI}\label{subsec:ai}
AI is large umbrella of terms which includes Natural Language Processing, Computer Vision, Machine Learning, Robotics,
Recommendation systems, or Large Language Models.
RouteChasm works only with LLMs to generate structured text responses for AI powered features.
LLMs can be simplified to a function that takes string as input on from the semantics of the text generates text response.
This project uses custom text prompts that provides additional information for the text input from the user.

\subsection{Framework vs. Library}\label{subsec:framework-vs-library}
The main difference lies in how the 3rd party code is used.
It can be simplified to library is being called explicitly by the programmer while framework calls the programmer's code
and handles main entry point of the application.
That is why projects can use many libraries but are limited to single framework.
Projects may use multiple frameworks, but the implementation leads to messy and inconsistent code.

\subsection{Full-stack Web Development}\label{subsec:fullstack-web-development}
The Web development can be simplified into two distinct parts, back-end and front-end code.
Back-end code implements business logic on the server, which includes, but it is not limited to request handling,
file serving, database communication, and server side rendering.
Front-end code is served to the user as HTML, CSS, and JavaScript files that are then parsed and executed in the browser.
Front-end developer implements the look and feel of the applications user interface.
Full-stack developer works on both front-end interfaces and back-end infrastructure.
Full-stack framework provides guidelines and code for both parts of the codebase.
